### 2018-07-17 doc/plos/text/manuscript.tex
add accuracy measure MASE
See also:
Hyndman RJ, Koehler AB. Another look at measures of forecast accuracy.
International journal of forecasting. 2006 Oct 1;22(4):679-88.

In a given location over a given period of time, we assess the accuracy of a
set of nowcasts by two measures: mean absolute error (MAE) and root mean
squared error (RMSE). With ground truth vector $\vec{x}$, nowcast vector
$\vec{y}$, and elements indexed by week $w$ of $n$, these measures are defined
as:

@@

@@

>>>>

In a given location over a given period of time, we assess the standalone
accuracy of a nowcast by two measures: mean absolute error (MAE) root mean
squared error (RMSE). With ground truth vector $\vec{x}$, nowcast vector
$\vec{y}$, and elements indexed by week $w$ of $n$, these measures are defined
as:

@@

Although the units of ground truth (i.e. wILI) are the same in all locations,
the normal range of wILI varies between locations. To facilitate comparison
between locations, we also report mean absolute scaled error (MASE)
\cite{hyndman2006another}. MASE is the MAE of a given nowcast normalized by the
MAE of a naive nowcast in the same location. We define the naive nowcast for
any given location on any given week as the reported ground truth in the same
location 52 weeks earlier. Using the same notation as above, and considering
the $m$ weeks for which ground truth is available for at least 52 weeks prior,
MASE is defined as:

\begin{align*}
  \text{MASE} &= \text{MAE} \left( \frac{1}{m} \sum_{w=1}^m{\left|x_w - x_{w - 52}\right|} \right) ^ {-1}
\end{align*}

@@

\bibitem{hyndman2006another}
Hyndman RJ, Koehler AB.
\newblock Another look at measures of forecast accuracy.
\newblock International journal of forecasting. 2006;22(4):679--688.
